Reionization Planck 2018 ...

### 2020-08-22 paper/rei.tex

\begin{figure}
\includegraphics[width=0.48\textwidth]{results/pc_results/plot_mj_triangle_pl18_pc_zmax30_pliklite_srollv2_vs_pl18_pc_zmax30_pliklite.pdf}
\caption{PC chains for zmax = 30 using Planck 2018 srollv2 likelihood vs Planck 2015.
}
\label{fig:plot_mjs}
\end{figure}

@@

\begin{figure}
\includegraphics[width=0.48\textwidth]{results/pc_results/plot_m1_m2_pl18_pc_zmax30_pliklite_srollv2_vs_pl18_pc_zmax30_pliklite_wTauTrajectory.pdf}
\caption{m1-m2 plane for zmax = 30 using Planck 2018 srollv2 likelihood vs Planck 2015.
}
\label{fig:plot_m1m2}
\end{figure}

>>>>

\begin{widetext}

\begin{figure}
\includegraphics[width=0.7\textwidth]{results/pc_results/plot_mj_triangle_pl18_pc_zmax30_pliklite_srollv2_vs_pl18_pc_zmax30_pliklite.pdf}
\caption{PC chains for zmax = 30 using Planck 2018 srollv2 likelihood vs Planck 2015.
}
\label{fig:plot_mjs}
\end{figure}

\end{widetext}

@@

\begin{figure}
\includegraphics[width=0.4\textwidth]{results/pc_results/plot_m1_m2_pl18_pc_zmax30_pliklite_srollv2_vs_pl18_pc_zmax30_pliklite_wTauTrajectory.pdf}
\caption{m1-m2 plane for zmax = 30 using Planck 2018 srollv2 likelihood vs Planck 2015.
}
\label{fig:plot_m1m2}
\end{figure}
